Data Formatting

### 2022-09-09 scripts/data_format.Rmd
fix filepath

Data
```{r}
here()
data <- read_csv(here("data/weighted_prev_competence_111220.csv"))
tree <- ape::read.nexus(here("data/asup_just_tree.txt"))
names <- read_csv(here("data/species_names_ids.csv"))
```

>>>>

Data
```{r}
here()
data <- read_csv(here("raw_data/weighted_prev_competence_111220.csv"))
tree <- ape::read.nexus(here("raw_data/asup_just_tree.txt"))
names <- read_csv(here("raw_data/species_names_ids.csv"))
```
